\setcounter{page}{4}
\addcontentsline{toc}{chapter}{\large Introduction}
\chapter*{Introduction}

	Hello to whoever will read this book of specifications which will introduce to you our game project.
	\\\\
	Our team is called the Suicide Squad and our project 'I WANNA DIE'.
	We will present you, in this book of specification, the different aspects of our project which is, trust me, a bit unusual .
	\\\\
	This game is born in the mind of Clément then Aymeric joined him in his quest , modifying a bit the original idea , then being friends with Thibaut and Thibault and them having no group, they decided to join the group. After some discussions, beers, and trepidant murders, we all mixed our ideas and then all agreed on the different aspects of this project.
	\\\\
	I WANNA DIE is a reflexion and platform game. The player will evolve in a rather friendly environment.
	In fact, we would like to create a game which has a different goal than the usual ones. The game consists of a set of levels where the aim is to kill yourself in order to go to the next harmless level. That turnaround in the usual game mechanics will affect all the game and may disturb the player during his gaming experience.
	\\\\
	The aim of this project is to exceed our skills to present, at the end, a result which we can be proud of. Furthermore,
	we will have to improve ourself in coding, and respect some restrictions that we will find again in the professional world.
	\\\\
	Well, this is the end of this introduction page to our project. We wish you a good reading ! :)	