\chapter{Individual Presentations}

	\section{Clément}

		I'm Clément Gillard, the group leader. The goal of this project is to make a functional game as a team,
		in a defined span of time. As a group, it will teach me how to efficiently work on a group project.
		As an individual member of the group, it will give me the ability to learn about
		and work on some technology and algorithms I might never have used without having this project
		to do as a part of my education at EPITA. As a group leader, it will teach me how to manage a team
		and its teamwork, just has I might have to do during my professional career as
		an information technology engineer.

	\section{Thibaut}

		I am Thibaut Chérel, and I am in the class E1 at EPITA. At the beginning of the year,
		I wanted to do a platform game, because I always loved this kind of games,
		but I had no idea about who should I do it with. Then I started to think about doing it with Thibault.
		We heard that Clément and Aymeric, who are both our friends, wanted to be together but they were only 2.
		So Thibault and I decided to join them. When Clément spoke about a suicide game, I was very excited.
		We made a lot debates to decide precisely what we would like our game to be.
		We finally decided to make a reflexion platform game, which looks like my first idea,
		and everyone was happy with this. I think the project will really help me to work in group,
		because it is not just a group work of a few weeks ; we will work on this project together during 6 months.
		We will need a good team work if we want to succeed and produce a good game.
		The project will also teach me a lot of things, which are needed for the game and that I, as of right now,
		have absolutely no idea how to do. Furthermore, a long project like this one also improve our ability to work
		in group and individually, because the project will be spread between us,
		and I will have to work alone on my part. So I am very excited about this project,
		just by thinking about all the knowledge I will acquire.

	\section{Aymeric}

		Hello world ! I'm Aymeric, 18 years old and already passionate by information technology.
		\\
		I believe that working in a group is a good way to improve yourself. In fact,
		it trains people to collaborate and make concessions. Furthermore, the aim of this project is
		to overpass myself to be able present, in the end, a good result of which i can be proud of.
		I would like too earn some skills too.
		\\
		I am in this group because I share the same idea with the other members.
		We all wanted to do something a bit different than usual games, while still being a classic platform
		and reflexion game like Portal is. Furthermore, I wanted to code a game which had a different goal
		than survive and win (like all platform game), that's the reason why I joined this group.
		\\
		We are all different, but we will all bring our qualities in this project and I am sure we will work well together.
		Clément is a great developer, and he is not afraid of difficulties. Thibaut is reactive and funny.
		Thibault is serious and motivated.
		\\
		I'm in charge of the level design because I would like to create the environment where the hero evolves.
		In every video game, the environment shows the atmosphere of the game,
		and that is something I really want to emphasize on .

	\section{Thibault}

		Shortly before the distribution of the "Project Information" file, I did not really have a project idea,
		nor a group to do it with. I just talked to Aymeric and Clément,
		they suggested to me their idea of a "suicide game", and I was really interested by this idea,
		it looked interesting to code, so they proposed me to join their group and I accepted.
		Personally this game will ask me concentration, effort and enough organization to finish this project.
		But I will also need to learn how to work with a group, organize myself with people and allocate tasks.
